Multisensor Architecture for an Intersection Management System

### 2018-06-01 ch3-arch_sys.tex
Added pol2cart description

\subsubsection{Preprocessing}
\begin{description}
\item[laser\_background\_remove]laser\_bg\_remove

@@

Let suppose we have N scans from the laser and $d_{\theta i}$ be the distance measure at angle $\theta$ in scan $i$. Thus, the background value for that angle $\theta$ is $bg_\theta = max( \{d_{\theta i} | 1 < i < N\})$ and the background model is $bg = \{bg_\theta | \theta \in \Theta\} $ where $\Theta$ is the set of angles of scanning, in this case from -90\degree to 90\degree with 0.5\degree step.
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/polar2cart.pdf}
\caption{polar\_to\_cartesian}
\label{polar_to_cartesian}
\end{figure}

>>>>

\subsubsection{Preprocessing}
\begin{description}
\item[laser\_background\_remove] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}

@@

Let suppose we have N scans from the laser and $d_{\theta i}$ be the distance measure at angle $\theta$ in scan $i$. Thus, the background value for that angle $\theta$ is $bg_\theta = max( \{d_{\theta i} | 1 < i < N\})$ and the background model is $bg = \{bg_\theta | \theta \in \Theta\} $ where $\Theta$ is the set of angles of scanning, in this case from -90\degree to 90\degree with 0.5\degree step.

\item[laser\_polar2cart] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/polar2cart.pdf}
\caption{polar\_to\_cartesian}
\label{polar_to_cartesian}
\end{figure}

This block takes as input a message of type laser\_pol\_msg for converting it into cartesian coordinates referenced to global system. For this reason, it also takes a laser\_cfg parameter to include laser position information in the conversion. Output message contains a set of x, y points obtained from the following equations:

\begin{eqnarray*}
O_x = I_\rho*\cos{\phi}+S_x \\
O_y = I_\rho*\sin{\phi} + S_y \\
\phi = I_\theta + S_\theta
\end{eqnarray*}

Where:

$(S_x, S_y, S_\theta)$: Position and orientation of the laser \\
$(I_\rho, I_\theta )$: Input message (distance and angle arrays) \\
$(O_x, O_y )$: Output message (x and y arrays) \\

\item[laser\_cart\_merge] \hfill
